Validation of marker gene expression

### 2025-02-26 analyses/cell-type-consensus/template-notebooks/marker-gene-validation.Rmd
keep HPC markers even though they aren't unique

# make a data frame that just has the unique genes 
# unique genes are those that are only observed in one cell type based on observance in Cell Marker 
# this was determined when creating the marker gene table from Cell Marker 
unique_gene_df <- group_stats_df |> 
  dplyr::filter(gene_observed_count == 1)
```

>>>>

# make a data frame that just has the unique genes 
# unique genes are those that are only observed in one cell type based on observance in Cell Marker 
# this was determined when creating the marker gene table from Cell Marker 
unique_gene_df <- group_stats_df |> 
  dplyr::filter(gene_observed_count == 1 | validation_group_annotation == "hematopoietic precursor cell")
```
